Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-15 writeup/gz_hubble_data.tex
Moving to past tense for Sections 2 and 3. Closes #97.

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
are selected from various \textit{Hubble Space Telescope} Legacy programs that
used the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
GOODS-S), with filters selected to probe the rest-frame optical emission from
galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go
down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of
$\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
morphological data include measurements of both bulge- and disk-dominated
galaxies, details on spiral disk structure that relate to the Hubble type, as
well as clump identification and geometry. This paper also describes and
employs a novel method for calibrating morphological bias by using
artificially-redshifted galaxy images as a baseline. The GZH catalog contains
both raw and calibrated morphological vote fractions for $150,771$ galaxies,
providing a comprehensive data set suitable for large-scale studies of galaxy
evolution. 
% didn't the GOODS-N and GOODS-S second phases go deeper than 23.5 mag? am I misremembering? --BDS

@@

The GZH project contains images drawn from a number of different dedicated
surveys and sample selection criteria. The majority of the data (as implied by
the project name) are taken directly from \hst{} Legacy Surveys, all of which
primarily use imaging from the Advanced Camera for Surveys (ACS). Results from
the individual surveys have been combined into a single photometric and
morphological database, the Advanced Camera for Surveys General Catalog
\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
Table~\ref{tbl:gzh_numbers}.

@@

\item The All-Wavelength Extended Groth Strip International Survey
    \citep[AEGIS;][]{dav07} covers a strip centered at
    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area was
    selected for a deep survey due to a combination of low extinction and low
    Galactic/zodiacal emission. The ACS images covered 63 separate tiles over a
    total area of $\sim710$~arcmin$^2$. The two ACS bands for AEGIS had exposure
    times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The
    final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For
    extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in
    \Vband{} and 25.61 (AB) in \Iband.

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covers two separate fields in the northern and southern hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch vary by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. Images are dithered to a pixel scale of 0.03~\arcsec/pixel and cover a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
    $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and
    25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of
    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consists of 1 orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590 total pointings are used to cover the entire
    field. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} is 24.7 mag.

\item The Galaxy Evolution from Morphologies and SEDs
    \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep
    Field-South. The GEMS data covers $\sim800$~arcmin$^2$, completely surrounding
    the area covered by GOODS-S. Images from ACS in GEMS have 1 orbit per pointing
    for a total of 63~pointings. The exposure times are 2160 and 2286~seconds in
    \Vband{} and \zband{}, respectively. The image resolution has a pixel scale
    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitudes for source
    detection are 25.7 AB in \Vband{} and 24.2~AB in \zband.

@@

In the ACS-GC \citep{gri12}, individual galaxies are identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH includes all galaxies with $m <
23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS,
GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
113,166~images (Table~\ref{tbl:gzh_numbers}).

Single-epoch images from SDSS Stripe~82 were selected using the same criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used are three-color composites using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag and the galaxies detected in the
single-depth images and matched to a co-add source. This resulted in a larger
set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
are dimmer than the initial magnitude cut of 17.77.

@@

The images used for classification in GZH are color-composite JPGs made from
multi-band data. The exact process for creating the images depends on the bands
and resolutions in the surveys.

For galaxies in the ACS-GC, color composites are made using a fixed pixel
intensity scaling with weights of
$[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue
channels respectively. A nonlinear mapping is applied to each pixel to
emphasize the contrast in faint features \citep{lup04}, taking the form of:

@@

\noindent The GZH images from \citet{gri12} use a value of $b=3$.

The majority of the data in Legacy surveys described in
Section~\ref{ssec:legacy_surveys} had images in only one or two filters
available when the GZH project was first launched, making standard 3-channel
RGB images in the same method used for the SDSS images in the original Galaxy
Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the
two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the
blue channel, the higher-wavelength band to the red channel, and the green
channel created by taking the geometric mean of the two. Bands used in each of
the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and
GOODS-S images use different filters --- this was a deliberate choice made so
that the GEMS images could be directly compared with the overlapping coverage
of GOODS-S (Figure~\ref{fig:filtercurves}).

@@

The COSMOS images only had the \Iband{} imaging available at the time of
classification in GZH. For these galaxies, we created ``pseudocolor'' images by
using the ACS \Iband{} data as the illumination map and ground-based imaging
from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the
color gradients \citep[see][for further details]{gri12}. This means that the
images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
overall intensity, but the color gradients are at ground-based resolution, with
seeing between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.

Stripe~82 single-epoch images were taken directly from the color composites on
the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and
$i^{\prime}$ exposures into the RGB channels. The co-added Stripe~82 images
were assembled from runs 106 and 206 in DR7 and made into color composites
using the method of \citet{lup04}.

To deal with images in which the sky noise was highly colored (which might have
been a distraction to visual classification), a soft-edged object mask was
applied that preserves the color balance for galaxies, but desaturates speckled
noise against regions of blank sky. This technique was applied only to the
co-added Stripe~82 and the COSMOS images.

@@

GZH also includes a set of images designed to measure the effect of active
galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
can have bright, unresolved optical emission, this has the potential to mimic
or distort the identification of a bulge component. The presence of an AGN is
simulated by modeling the point spread function (PSF) of the telescope and then
inserting a bright source near the center of a real galaxy. For each image, the
simulated AGN is assigned one of three colors -- either blue, red, or flat
(white) as seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images
with different simulated AGN for each host.

@@

Photometric data for the bulk of the GZH sample is largely drawn from the
tables provided in \citet{gri12}. This includes photometric parameters such as
the fluxes, magnitudes, radii, ellipticities, position angles, and positions
drawn from both \sextractor{} and \galfit. \galfit{} also provides the
parametric \sersic{} index and effective half-light radius for the best-fit
model. All parameters are measured in both bands of the ACS imaging, with the
exception of the single-band COSMOS images.

Redshifts for the GZH catalog are compiled from a variety of sources. For each
galaxy, the primary redshift used for debiasing calculations
(Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of
Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
$\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt
Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the
following algorithm is used to select the $\tt Z\_BEST$ quantity. This first
priority is spectroscopic redshifts; these are provided in the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A high
quality spectroscopic redshift in the ACS-GC is the primary option; if none is
available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and
then MUSYC. For galaxies with multiple spectroscopic redshifts, more than 98\%
are consistent at $\Delta z<0.001$, and so the order of selection makes no
practical difference. If no spectroscopic redshifts are available, the
1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift
with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken
from the CasJobs DR7 tables. This includes $ugriz$ Petrosian magnitudes and
fluxes, as well as the relative de~Vaucouleurs and exponential fits from the
model magnitudes. Redshifts used for the SDSS galaxies are all spectroscopic.
82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the
co-add images have a measured DR7 spectroscopic redshift.

@@

\subsection{User weighting}\label{ssec:weighting} The votes of individual users
who classified galaxies in GZH are combined to make a vote fraction for each
response to a question ($f_{response}$) on the classification tree. Users'
votes are weighted slightly \citep[in a method identical to that described
in][]{wil13} such that users who frequently disagree with all other users end
up having very low weights. The user weighting $(w)$ is 1 for the top 95\% of
users as ranked by consistency. For the bottom 5\% of users, $w$ drops smoothly
and is effectively zero for only the bottom 1\% of classifiers in the CDF.
Since this only affects a tiny percentage of the users (and an even smaller
percentage of the classifications) the overall effect on the GZH dataset is
minimal. This method is effective, however, at filtering out contributions from
random or deliberately malicious classifiers.

Classifications for a particular user are aggregated and weighted only if they
were logged into GZH under their username (which is encouraged, but not
required for participation). Classifications by users not logged in are marked
as ``Anonymous''; no weighting is applied to these classifications, but they
are otherwise treated identically in the data processing.

@@

Classifications for GZH are made using a web-based interface
(Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
The front-end runs on a Ruby~on~Rails framework with classifications stored in
a MySQL backend. Users are shown a randomly-selected color composite image from
the GZH sample; the default shows the image with a black sky background,
although users have the options to invert the color palette if desired. The
questions and responses for morphology appear on the right side of the image as
a panel, including both text and icons. There is no tutorial required for
participation, although users can access an extensive ``Help'' section
containing example images and descriptive text for all the morphological
labels.

@@

The procedure for classifying an image in GZH follows a hierarchical decision
tree (Figure~\ref{fig:decisiontree}). Every classification begins with the user
identifying whether the object at the center of the image is a smooth galaxy, a
galaxy with a disk or other features, or a star/artifact. Subsequent questions
in the tree depend on the previous answer(s) given by the user; the structure
of the decision tree is designed so that the user will answer every question
relevant to the morphology that they have identified. Questions that are not
answered are implicitly assumed to be absent in the image --- for example, if
the user identifies a galaxy as being smooth, they are not asked to count the
number of spiral arms. For every task, the user chooses a single answer before
continuing to the next question; they have also the option to restart a
classification in-progress if a mistake has been made.

The GZH decision tree has four broad sets of morphologies classified by the
users. The first option is designating the object as a star or image artifact
(the result of either bad data or incorrect classification by the ACS pipeline
as a galaxy); in this case, the classification ends and no further questions
are asked. The second set are smooth galaxies, intended to select
ellipticals/early-types; users also measure the relative axial ratio
(roundness) for these galaxies. The third set is for disk/late-type galaxies,
which measures the features necessary to place a galaxy on the standard Hubble
tuning fork (bars, spiral arm, strength of the central bulge). The final set,
which is new to the high-redshift targets in GZH, asks users to identify
objects dominated by clumpy morphologies. Further annotations for these
galaxies includes assessing the number, arrangement, relative brightness, and
location of the clumps within the galaxy. Finally, every classification of a
galaxy gives users the option of identifying ``odd'' features within the image;
these labels are for relatively rare $(\lesssim1\%)$ phenomena, including dust
lanes, gravitational lenses, and mergers.

The number of independent classifications per subject collected by GZH is on
average higher than GZ1 or GZ2, due to both the increased complexity of the
decision tree and the relative difficulty of classifying images of small and
distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets have a
median of 122~independent classifications per image. The remainder of the
images either had a later activation date (COSMOS, simulated AGN) or by a lower
retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these
samples have a median of 46--48~classifications per image
(Figure~\ref{fig:classification_hist}).

>>>>

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various \textit{Hubble Space Telescope} Legacy programs that
used the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and
GOODS-S), with filters selected to probe the rest-frame optical emission from
galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go
down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of
$\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH
morphological data include measurements of both bulge- and disk-dominated
galaxies, details on spiral disk structure that relate to the Hubble type, as
well as clump identification and geometry. This paper also describes and
employs a novel method for calibrating morphological bias by using
artificially-redshifted galaxy images as a baseline. The GZH catalog contains
both raw and calibrated morphological vote fractions for $150,771$ galaxies,
providing a comprehensive data set suitable for large-scale studies of galaxy
evolution. 
% didn't the GOODS-N and GOODS-S second phases go deeper than 23.5 mag? am I misremembering? --BDS

@@

The GZH project contains images drawn from a number of different dedicated
surveys and sample selection criteria. The majority of the data (as implied by
the project name) were taken directly from \hst{} Legacy Surveys, all of which
primarily used imaging from the Advanced Camera for Surveys (ACS). Results from
the individual surveys have been combined into a single photometric and
morphological database, the Advanced Camera for Surveys General Catalog
\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
Table~\ref{tbl:gzh_numbers}.

@@

\item The All-Wavelength Extended Groth Strip International Survey
    \citep[AEGIS;][]{dav07} covers a strip centered at
    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area
    of the sky was selected for a deep survey due to a combination of low
    extinction and low Galactic/zodiacal emission. The ACS images covered 63
    separate tiles over a total area of $\sim710$~arcmin$^2$. The two ACS bands
    for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and
    2100~seconds in F814W (\Iband). The final mosaic images were dithered
    to a resolution of 0.03~\arcsec/pixel. For extended objects, the
    limiting magnitude of sources was 26.23~(AB) in \Vband{} and 25.61 (AB) in
    \Iband.

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covered two separate fields in the northern and southern hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
    25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consisted of 1~orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590 total pointings were used to cover the entire
    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} was 24.7 mag.

\item The Galaxy Evolution from Morphologies and SEDs
    \citep[GEMS;][]{rix04,cal08} survey was also centered on the Chandra Deep
    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
    the area covered by GOODS-S. Images from ACS in GEMS had 1 orbit per pointing
    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
    detection was 25.7 AB in \Vband{} and 24.2~AB in \zband.

@@

In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
113,166~images (Table~\ref{tbl:gzh_numbers}).

Single-epoch images from SDSS Stripe~82 were selected using the same criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
single-depth images and matched to a co-add source. This resulted in a total
set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

The images used for classification in GZH were color-composite JPGs made from
multi-band data. The exact process for creating the images depended on the bands
and resolutions in the surveys.

For galaxies in the ACS-GC, color composites were made using a fixed pixel
intensity scaling with weights of
$[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue
channels respectively. A nonlinear mapping was applied to each pixel to
emphasize the contrast in faint features \citep{lup04}, taking the form of:

@@

\noindent GZH images from \citet{gri12} used a value of $b=3$.

The majority of the data in Legacy surveys described in
Section~\ref{ssec:legacy_surveys} had images in only one or two filters
available when the GZH project was first launched, making standard 3-channel
RGB images in the same method used for the SDSS images in the original Galaxy
Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the
two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the
blue channel, the higher-wavelength band to the red channel, and the green
channel created by taking the geometric mean of the two. Bands used in each of
the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and
GOODS-S images used different filters --- this was a deliberate choice made so
that the GEMS images could be directly compared with the overlapping coverage
of GOODS-S (Figure~\ref{fig:filtercurves}).

@@

The COSMOS images only had the \Iband{} imaging available at the time of
classification in GZH. For these galaxies, GZH used ``pseudocolor'' images
created by using the ACS \Iband{} data as an illumination map and ground-based
imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to
provide the color gradients \citep[see][for further details]{gri12}. This
resulted in images with the angular resolution of \hst{}
($\sim0.05$~\arcsec/pixel) for the overall intensity, but color gradients at
ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{}
\citep{tan07}.

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and made into color composites using the method of \citet{lup04}.

To deal with situations in which the sky noise was highly colored (which might
have been a distraction to visual classification), a soft-edged object mask was
applied to the coadded Stripe~82 and the COSMOS images. This mask preserved the
color balance for galaxies, but desaturated speckled noise against regions of
blank sky.

@@

GZH also included a set of images designed to measure the effect of active
galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
can have bright, unresolved optical emission, AGN have the potential to mimic
or distort the identification of a bulge component. The presence of an AGN was
simulated by modeling the point spread function (PSF) of the telescope and then
inserting a bright source near the center of a real galaxy. For each image, the
simulated AGN was assigned one of three colors -- either blue, red, or flat
(white) as seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host.

@@

Photometric data for the bulk of the GZH sample were largely drawn from the
tables in \citet{gri12}. This included photometric parameters such as
the fluxes, magnitudes, radii, ellipticities, position angles, and positions
drawn from both \sextractor{} and \galfit. \galfit{} also provided the
parametric \sersic{} index and effective half-light radius for the best-fit
model. All parameters were measured in both bands of the ACS imaging, with the
exception of the single-band COSMOS images.

Redshifts for the GZH catalog were compiled from a variety of sources. For each
galaxy, the primary redshift used for debiasing calculations
(Section~\ref{sec:debiasing}) is in the $\tt Z\_BEST$ column of
Table~\ref{tbl:catalog_hst}. The redshift type (spectroscopic: $\tt SPEC\_Z$,
photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column
$\tt Z\_BEST\_TYPE$, and the source catalog of the redshift is included as $\tt
Z\_BEST\_SOURCE$.

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
priority is spectroscopic redshifts; these were taken from the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
high-quality spectroscopic redshift in the ACS-GC is the primary option; if
none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
made no practical difference. If no spectroscopic redshifts were available,
the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

Photometric and spectroscopic data for the SDSS Stripe~82 galaxies were taken
from the CasJobs DR7 tables. This included $ugriz$ Petrosian magnitudes and
fluxes, as well as the relative de~Vaucouleurs and exponential fits from the
model magnitudes. All redshifts used for SDSS galaxies were spectroscopic.
82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the
co-add images had a measured DR7 spectroscopic redshift.

@@

\subsection{User weighting}\label{ssec:weighting}

The votes of individual users who classified galaxies in GZH were combined to
make a vote fraction for each response ($f_{response}$) to a question in the
classification tree. Users' votes were weighted \citep[in a method identical to
that described in][]{wil13} such that users who frequently disagreed with all
other users ended up having very low weights. The user weighting $(w)$ was 1
for the top 95\% of users, as ranked by consistency. For the bottom 5\% of
users, $w$ was designed to drop smoothly and was effectively zero for the
bottom 1\% of classifiers.  Since this only affected a tiny percentage of
the users (and an even smaller percentage of the classifications) the
overall effect on the GZH dataset was minimal. The method was effective,
however, at filtering out contributions from random or deliberately
malicious classifiers.

Classifications each user were aggregated and weighted only if they
were logged into GZH under their username (which was encouraged, but not
required for participation). Classifications by users not logged in were marked
as ``Anonymous''; no weighting was applied to these classifications, but they
were otherwise treated identically in the data processing.

@@

Classifications for GZH were made using a web-based interface
(Figure~\ref{fig:interface}), similar in design to Galaxy~Zoo and Galaxy~Zoo~2.
The front-end runs on a Ruby~on~Rails framework with classifications stored in
a MySQL backend. Users were shown a randomly-selected color composite image from
the GZH sample; the default showed the image with a black sky background,
although users had the option to invert the color palette if desired. The
questions and responses for morphology appeared on the right side of the image as
a panel, including both text and icons. There was no tutorial required for
participation, although users could access an extensive ``Help'' section
containing example images and descriptive text for all the morphological
labels.

@@

The procedure for classifying an image in GZH followed a hierarchical decision
tree (Figure~\ref{fig:decisiontree}). Every classification began with the user
identifying whether the object at the center of the image was a smooth galaxy,
a galaxy with a disk or other features, or a star/artifact. Subsequent
questions in the tree depended on the previous answer(s) given by the user; the
decision tree as designed so that the user answered every question relevant to
the morphology in the process of being identified. Questions that were not
answered were implicitly assumed to be absent in the image --- for example, if
the user identified a galaxy as being smooth, they were not asked to count the
number of spiral arms. For every task, the user chose a single answer before
continuing to the next question; they also had the option to restart any
classification in-progress.

The GZH decision tree had four broad sets of morphologies classified by the
users. The first option designated stars or image artifacts
(the result of either bad data or incorrect classification by the ACS pipeline
as a galaxy); in this case, the classification process ended and no further questions
were asked of the user. The second set were smooth galaxies, intended to select
ellipticals/early-types; users also measure the relative axial ratio
(roundness) for these galaxies. The third set was for disk/late-type galaxies,
which measured the features necessary to place a galaxy on the standard Hubble
tuning fork (bars, spiral arm, strength of the central bulge). The final set,
which was new in this phase of Galaxy~Zoo and designed for high-redshift targets, asked users to identify
objects dominated by clumpy morphologies. Further annotations for clumpy
galaxies included assessing the number, arrangement, relative brightness, and
location of the clumps within the galaxy. Finally, every classification of a
galaxy gave users the option of identifying ``odd'' features within the image;
these labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
lanes, gravitational lenses, and mergers.

The number of independent classifications per subject collected by GZH was on
average higher than GZ1 or GZ2, due to both the increased complexity of the
decision tree and the relative difficulty of classifying images of small and
distant galaxies. Images from the main AEGIS, GEMS, and GOODS data sets had a
median of 122~independent classifications per image. The remainder of the
images either had a later activation date (COSMOS, simulated AGN) or a lower
retirement limit (the low-redshift SDSS Stripe~82 galaxies). Images from these
samples had a median of 46--48~classifications per image
(Figure~\ref{fig:classification_hist}).
